---
output: html_document
editor_options: 
  chunk_output_type: inline
---
# ---------------------------------------------------------
# This is the analysis for the study, mainly contains: interaction effect, confident interval, time plot
# ---------------------------------------------------------

# Preparation
Import packages and set global configuration variables.
```{r eval=FALSE}
# Load the magic package
source('analysis.R')
library(forcats)
library(tidyverse)
file_study_folder <- "./data/pilot/"
save_img_sign <- TRUE

saveImg <- function(name){
  if(save_img_sign){
    ggsave(name, width = 10, height = 6, useDingbats=FALSE)
  }
}
```

# Task: co-Saliency
## Import and pre-process the user data
```{r}
# Get the list of files.
file_path <- paste(file_study_folder, "co-saliency", '', sep = "/")#
filelist <- list.files(path = file_path, pattern = '*coSaliency.*?\\.csv$')

# Compute data_total
data_total <- rbind()
total_time <- c()
for (file in filelist) {
  print(file)
  # read data
  data_temp <- read.csv(paste(file_path, file, sep = ""), header = TRUE) %>%
    # Remove duplicated rows with extremely long time
    filter(totalTime < 1000)

  # Remove another type of duplicated rows, if any
  test <- data_temp %>%
    group_by(userName, fileId, conditionId, changeMagnitude, changeType) %>%
    summarise(count = n())
  if(nrow(test) != nrow(data_temp)) {
    # Print the dataframe if there're duplicated rows.
    print(data_temp)
    print(test)
    data_temp <- data_temp %>%
      group_by(userName, fileId, conditionId, changeMagnitude, changeType) %>%
      slice(c(n())) %>%
      ungroup()
  }
  xx <- strsplit(file, "-")
  group_id <- xx[[1]][1]
  
  data_temp <- data_temp %>%
    mutate(errorTime=ifelse(userResult!=1, totalTime, 0)) %>%
    mutate(accuracy=userResult) %>%
    mutate(datasetGroup = rep(as.numeric(group_id),times=nrow(data_temp)))

  
  for(i in 1:nrow(data_temp)){
    user_result <- as.numeric(unlist(strsplit(as.vector(data_temp[i,]$clickOrder), "-")))
    right_result <- as.numeric(unlist(strsplit(as.vector(data_temp[i,]$rightAnswer), "-")))
    intersect_elements <- intersect(user_result, right_result)
    #print(right_result)
    #print(intersect_elements)
    #print(length(intersect_elements))
    data_temp[i,]$accuracy <- length(intersect_elements)/length(right_result)
    
    #print(data_temp[i,]$accuracy)
  }
  
  # sum the time of each user
  total_time <- c(total_time, sum(data_temp$totalTime))
  
  
  
  # bind the data to the total data frame
  data_total <- rbind(data_total, data_temp)
  
  # check each data: error rate of each condition
  group_data <- dplyr::summarise(group_by(data_temp,conditionId, userResult),count=n(), time=sum(totalTime))
  group_data_total <- dplyr::summarise(group_by(data_temp,conditionId),count=n(), time=sum(totalTime))
  for(i in 1:nrow(group_data_total)){
    x <- group_data_total[i,]
    x1 <- group_data[group_data$conditionId==x["conditionId"][[1]] & group_data$userResult==0,]
    if(nrow(x1)==0){
      cat(toString(x["conditionId"][[1]]), " error rate is ", 0, ", time is ",x["time"][[1]],"\n")
    }else{
      cat(toString(x["conditionId"][[1]]), " error rate is ", x1["count"][[1]]/x["count"][[1]], ", time is ",x1["time"][[1]],"\n")
    }
  }
  
  data_t <- data_temp[data_temp$conditionId==-1 & data_temp$userResult==0, ]
  cat("distractor trials error rate is ", nrow(data_t)/4,"\n")
  if(nrow(data_t)/4>0){
    print("=============================")
  }
  
  data_t <- data_temp[data_temp$totalTime==60, ]
  if(nrow(data_t)/nrow(data_temp)>0){
    cat("totalTime==60 rate is ", nrow(data_t)/nrow(data_temp),"\n")
    print("=============================")
  }
  
  if(nrow(data_temp)!=40){
    print(nrow(data_temp))
    print("*********************************")
  }
}
#write.csv(data_total, paste(file_path, "statics.csv", sep = ""))
cat("\n", "average time is ", toString(mean(total_time)/60), "min\n")
mean_time <- (sum(total_time)-max(total_time)-min(total_time))/(length(total_time)-2)
cat("average time (remove max and min) is ", toString(mean_time/60), "min\n")
cat("max time is ", toString(max(total_time)/60), "min\n")
cat("min time is ", toString(min(total_time)/60), "min\n")

# Uncomment if want to check the trial numbers per participant.
# temp <- data_total %>%
#   group_by(userName) %>%
#   summarise(trials = n()) %>%
#   filter(trials != 30)

# Compute variables like error
data_total <- data_total %>%
  mutate(error=ifelse(userResult!=0, 0, 1)) %>%
  mutate(datasetId=fileId)

# removing the distractors
data_total <- data_total[data_total$conditionId!=-1, ]

# Prep Plot Consistency
data_total <- data_total %>%
  mutate(conditionName = conditionId) %>%
  mutate(conditionMagnitude = conditionId)
data_total[data_total$conditionId==0, ]$conditionName <- "Random Assignment"
data_total[data_total$conditionId==1, ]$conditionName <- "Optimized Assignment"
data_total[data_total$conditionId==2, ]$conditionName <- "Alpha Blending"
data_total[data_total$conditionId==3, ]$conditionName <- "C3-Palette Assignment"
data_total[data_total$conditionId==4, ]$conditionName <- "Palettailor"
data_total[data_total$conditionId==5, ]$conditionName <- "C3-Palette Generation"

data_total <- data_total %>%
  mutate(conditionName = fct_relevel(conditionName, 
                                 "C3-Palette Generation",
                                 "Palettailor", "C3-Palette Assignment", 
                                 "Alpha Blending", "Optimized Assignment", "Random Assignment"))

condition_names <- c("Random Assignment", "Optimized Assignment", "Alpha Blending", "C3-Palette Assignment", "Palettailor", "C3-Palette Generation")
# 0 is small, 1 is medium, 2 is large
for(i in 1:6){
  for(j in 0:2){
    data_total[data_total$conditionId==(i-1) & data_total$changeMagnitude==j, ]$conditionMagnitude <- paste(condition_names[i], j, sep = "-")
  }
}


# check which data of Ours generation is wrong
ours_data_error <- data_total[data_total$conditionId==5 & data_total$userResult==0, ]

# compute the time threshold
data_time_correct <- data_total[data_total$userResult==1, ]
data_time_threshold_correct <- data_total[data_total$totalTime<=30 & data_total$userResult==1, ]
threshold <- nrow(data_time_threshold_correct)/nrow(data_time_correct)
print(threshold)

```

```{r}
# find which trial has the most error
group_data_error <- dplyr::summarise(group_by(data_total,fileId, conditionName, error),count=n(), time=sum(totalTime))

```

## Check the interaction effect of Dataset x Condition
```{r}

data <- data_total

# Model1: error ~ ... datasetGroup + paletteName ...
model <- lm(error ~ conditionName + datasetGroup + conditionName * datasetGroup, data)
anova(model)
summary(model)

# Model2: error ~ ... condition + magnitude ...
model <- lm(error ~ conditionName + changeMagnitude + conditionName * changeMagnitude, data)
anova(model)
summary(model)

# Model3: for each change type: error ~ ... condition + magnitude ...
model <- lm(error ~ conditionName + changeMagnitude + conditionName * changeMagnitude, data[data$changeType=="pos", ])
anova(model)
summary(model)
# Model3: for each change type: error ~ ... condition + magnitude ...
model <- lm(error ~ conditionName + changeMagnitude + conditionName * changeMagnitude, data[data$changeType=="num", ])
anova(model)
summary(model)
```



## CI Plots and Statistical Tests
```{r}

# Generate the result table for error in the discrimination tasks.
stat_table_m <- function(data) {
  columns <- c("Condition", "μ~95%CI", "W", "p-value", "d")
  conditions <- levels(data$conditionName) %>% rev
  print(conditions)
  df_stats <- matrix("", ncol = length(columns), nrow = length(conditions)) %>% 
    data.frame() %>% 
    mutate_if(is.factor, as.character)
  names(df_stats) <- columns
  df_stats$Condition <- conditions
  print(conditions)
  
  for (index in 1:length(conditions)) {
    current_condition <- conditions[index]
    sub_data_one_group <- data %>% filter(conditionName==current_condition)
    # 95%CI
    df_stats[index, "μ~95%CI"] <- reportCI(sub_data_one_group, "error")
    
    if(current_condition != "C3-Palette Generation") {
      sub_data_two_groups <- data %>% filter(conditionName=="C3-Palette Generation" | conditionName==current_condition)
      # W test
      wt <- wilcox.test(error ~ conditionName, 
                        data = sub_data_two_groups, 
                        conf.int=TRUE)
      df_stats[index, "W"] <- as.character(wt$statistic)
      df_stats[index, "p-value"] <- format(wt$p.value, format = "e", digits = 2)
      
      # alternative report: with breaks.
      # if(wt$p.value < 0.05) { df_stats[index, "p-value"] <- "< 0.05"}
      # if(wt$p.value < 0.01) { df_stats[index, "p-value"] <- "< 0.01"}
      # if(wt$p.value < 0.001) { df_stats[index, "p-value"] <- "< 0.001"}
      # else { df_stats[index, "p-value"] <- "≥ 0.05" }
      
      # Effect size
      df_stats[index, "d"] <- reportES(sub_data_two_groups, "error", "conditionName")
    }
  }
  print(df_stats)
  
  return(df_stats)
}

data <- data_total

# #Statistical Test Results: mu~95% CI, W, p-value, d.
#df_stat_output <- stat_table_m(data)
#df_stat_output


ciplot(data, "error", "conditionName", "Total")
saveImg("results/cosaliency-error-conditionName-total.pdf")
ciplot(data, "accuracy", "conditionName", "Total")
saveImg("results/cosaliency-accuracy-conditionName-total.pdf")
ciplot(data, "totalTime", "conditionName", "Total")
saveImg("results/cosaliency-totalTime-conditionName-total.pdf")


data <- data %>%
  mutate(conditionMagnitude = fct_relevel(conditionMagnitude, 
                                 "C3-Palette Generation-0", "Palettailor-0", "C3-Palette Assignment-0", "Alpha Blending-0", "Optimized Assignment-0", "Random Assignment-0",
                                 "C3-Palette Generation-1", "Palettailor-1", "C3-Palette Assignment-1", "Alpha Blending-1", "Optimized Assignment-1", "Random Assignment-1",
                                 "C3-Palette Generation-2", "Palettailor-2", "C3-Palette Assignment-2", "Alpha Blending-2", "Optimized Assignment-2", "Random Assignment-2"))

ciplotManual(data, "error", "conditionMagnitude", "Magnitude")
saveImg("results/cosaliency-error-conditionMagnitude-total.pdf")
ciplotManual(data, "accuracy", "conditionMagnitude", "Magnitude")
saveImg("results/cosaliency-accuracy-conditionMagnitude-total.pdf")
ciplotManual(data, "totalTime", "conditionMagnitude", "Magnitude")
saveImg("results/cosaliency-totalTime-conditionMagnitude-total.pdf")

ciplot(data[data$changeType=="pos", ], "error", "conditionName", "pos")
saveImg("results/cosaliency-error-conditionName-pos.pdf")
ciplot(data[data$changeType=="pos", ], "totalTime", "conditionName", "pos")
saveImg("results/cosaliency-totalTime-conditionName-pos.pdf")

ciplot(data[data$changeType=="num", ], "error", "conditionName", "num")
saveImg("results/cosaliency-error-conditionName-num.pdf")
ciplot(data[data$changeType=="num", ], "totalTime", "conditionName", "num")
saveImg("results/cosaliency-totalTime-conditionName-num.pdf")

ciplotManual(data[data$changeType=="pos", ], "error", "conditionMagnitude", "pos")
saveImg("results/error-conditionMagnitude-pos.pdf")
ciplotManual(data[data$changeType=="pos", ], "totalTime", "conditionMagnitude", "pos")
saveImg("results/cosaliency-totalTime-conditionMagnitude-pos.pdf")

ciplotManual(data[data$changeType=="num", ], "error", "conditionMagnitude", "num")
saveImg("results/cosaliency-error-conditionMagnitude-num.pdf")
ciplotManual(data[data$changeType=="num", ], "totalTime", "conditionMagnitude", "num")
saveImg("results/cosaliency-totalTime-conditionMagnitude-num.pdf")

# 
# # Boxplot for using time of each palette name 
# boxplot(data, "errorTime", "condition")
# boxplot(data, "totalTime", "condition")
#ggsave("results/counting_time_box.pdf", useDingbats=FALSE)

# 
# library(gridExtra)
# tt1 <- ttheme_minimal(base_colour = '#636363', base_size = 15, padding = unit(c(5, 10), "mm"))
# #pdf("results/counting_stats.pdf", height=4, width=6)
# grid.arrange(
#   tableGrob(df_stat_output %>% select(-Condition), theme=tt1),
#   nrow=1)
# dev.off()

```


## grouped bar chart - error
```{r}
# define the render function
drawGroupedBarchartError <- function(used_data, title){
  group_data <- dplyr::summarise(group_by(used_data,changeMagnitude, conditionName, error),count=n())
  group_data_total <- dplyr::summarise(group_by(used_data,changeMagnitude, conditionName),count=n())

  specie <- c(rep("small" , 6) , rep("medium" , 6) , rep("large" , 6))
  condition <- c()
  value <- c()
  for(i in 1:nrow(group_data_total)){
    x <- group_data_total[i,]
    condition <- c(condition, as.character(x["conditionName"][[1]]))
    #cat(row_count, x["changeMagnitude"][[1]], x["conditionName"][[1]], "\n")
    x1 <- group_data[group_data$changeMagnitude==x["changeMagnitude"][[1]] & group_data$conditionName==x["conditionName"][[1]] & group_data$error==1,]
    if(nrow(x1)==0){
      value <- c(value, 0)
    }else{
      value <- c(value, x1["count"][[1]]/x["count"][[1]])
    }
  }
  grouped_data <- data.frame(specie,condition,value)
  grouped_data$specie <- factor(grouped_data$specie, levels = c("small", "medium", "large"))
  
  ggplot(grouped_data, aes(fill=condition, y=value, x=specie)) +
    geom_bar(position="dodge", stat="identity") +
    #scale_fill_manual(values = c("#4e79a7","#59a14f","#e15759")) +
    ggtitle(paste(title, ": magnitude-condition-error")) +
    xlab("magnitude") +
    ylab("error")
  
}

reference <- condition_names
data <- data_total[order(factor(data_total$conditionName, levels = reference)),]
drawGroupedBarchartError(data, "Total")

type_data <- data_total[data_total$changeType=="num",]
data <- type_data[order(factor(type_data$conditionName, levels = reference)),]
drawGroupedBarchartError(data, "number")

type_data <- data_total[data_total$changeType=="pos",]
data <- type_data[order(factor(type_data$conditionName, levels = reference)),]
drawGroupedBarchartError(data, "position")


```

## grouped bar chart - total time
```{r}
# define the render function
drawGroupedBarchartTime <- function(used_data, title){
  group_data <- dplyr::summarise(group_by(data,changeMagnitude, condition),count=sum(totalTime))
  specie <- c(rep("small" , 5) , rep("medium" , 5) , rep("large" , 5))
  condition <- c()
  value <- c()
  for(i in 1:nrow(group_data)){
    x <- group_data[i,]
    condition <- c(condition, x["condition"][[1]])
    value <- c(value, x["count"][[1]])
  }
  grouped_data <- data.frame(specie,condition,value)
  grouped_data$specie <- factor(grouped_data$specie, levels = c("small", "medium", "large"))
  
  ggplot(grouped_data, aes(fill=condition, y=value, x=specie)) +
    geom_bar(position="dodge", stat="identity") +
    #scale_fill_manual(values = c("#4e79a7","#59a14f","#e15759")) +
    ggtitle(paste(title, ": magnitude-condition-time")) +
    xlab("magnitude") +
    ylab("totalTime")
}

reference <- c("Random Tableau 10", "Random Tableau 20", "Ours Tableau 10", "Ours Tableau 20", "Ours Generation")
data <- data_total[order(factor(data_total$condition, levels = reference)),]
drawGroupedBarchartTime(data, "Total")

type_data <- data_total[data_total$changeType=="point number",]
data <- type_data[order(factor(type_data$condition, levels = reference)),]
drawGroupedBarchartTime(data, "point number")

type_data <- data_total[data_total$changeType=="shape",]
data <- type_data[order(factor(type_data$condition, levels = reference)),]
drawGroupedBarchartTime(data, "shape")

type_data <- data_total[data_total$changeType=="center position",]
data <- type_data[order(factor(type_data$condition, levels = reference)),]
drawGroupedBarchartTime(data, "center position")

```


## Power Analysis
### error
```{r}
data <- data_total#[data_total$changeType=="pos", ]

#error
df1 <- data %>% 
  filter(conditionName == "C3-Palette Generation") %>% 
  select(error) 
df2 <- data %>%
  filter(conditionName == "Random Assignment") %>% 
  select(error) 

abs(mean(df1$error) - mean(df2$error))
df <- df1 %>% rbind(df2)

powerAnalysisGraph(mean(df1$error), mean(df2$error), sd(df$error))
saveImg("results/cosaliency-error-conditionName-powerAnalysis.pdf")
```

### Time
```{r}
data <- data_total#[data_total$changeType=="center position", ]

#time
df1 <- data %>% 
  filter(conditionName == "C3-Palette Generation") %>% 
  select(totalTime) 
df2 <- data %>%
  filter(conditionName == "Random Assignment") %>% 
  select(totalTime) 

abs(mean(df1$totalTime) - mean(df2$totalTime))
df <- df1 %>% rbind(df2)

powerAnalysisGraph(mean(df1$totalTime), mean(df2$totalTime), sd(df$totalTime))
saveImg("results/cosaliency-totalTime-conditionName-powerAnalysis.pdf")
```




# Task: co-separability
## Import and pre-process the user data
```{r}
# Get the list of files.
file_path <- paste(file_study_folder, "co-separability", "", sep = "/")
filelist <- list.files(path = file_path, pattern = '*coSeparability.*?\\.csv$')

# Compute data_total
data_total <- rbind()
total_time <- c()
for (file in filelist) {
  print(file)
  # read data
  data_temp <- read.csv(paste(file_path, file, sep = ""), header = TRUE) %>%
    # Remove duplicated rows with extremely long time
    filter(totalTime < 1000)

  # Remove another type of duplicated rows, if any
  test <- data_temp %>%
    group_by(userName, fileId, conditionId, changeMagnitude) %>%
    summarise(count = n())
  if(nrow(test) != nrow(data_temp)) {
    print("------------------------")
    # Print the dataframe if there're duplicated rows.
    print(data_temp)
    print(test)
    data_temp <- data_temp %>%
      group_by(userName, fileId, conditionId, changeMagnitude) %>%
      slice(c(n())) %>%
      ungroup()
  }
  xx <- strsplit(file, "-")
  group_id <- xx[[1]][1]
  
  
  # sum the time of each user
  total_time <- c(total_time, sum(data_temp$totalTime))
  
  
  data_t <- data_temp[data_temp$conditionId==-1 & data_temp$userResult!=6, ]
  cat("distractor trials error rate is ", nrow(data_t)/4,"\n")
  if(nrow(data_t)/4>0){
    print("=============================")
  }
  
  data_t <- data_temp[data_temp$totalTime==60, ]
  cat("totalTime==60 rate is ", nrow(data_t)/nrow(data_temp),"\n")
  if(nrow(data_t)/nrow(data_temp)>0){
    print("=============================")
  }
  print(nrow(data_temp))
  
  if(nrow(data_temp)!=40){
    print("*********************************")
  }
  
  # removing the distractors
  data_temp <- data_temp[data_temp$conditionId!=-1, ]
  data_temp <- data_temp %>%
    mutate(error=ifelse(userResult==8, 0, 1)) %>%
    mutate(accuracy=abs(userResult-8)) %>%
    mutate(datasetGroup = rep(as.numeric(group_id),times=nrow(data_temp)))
  
  # bind the data to the total data frame
  data_total <- rbind(data_total, data_temp)
  
  # check each data: error rate of each condition
  group_data <- dplyr::summarise(group_by(data_temp,conditionId, error),count=n(), time=sum(totalTime))
  group_data_total <- dplyr::summarise(group_by(data_temp,conditionId),count=n(), time=sum(totalTime))
  for(i in 1:nrow(group_data_total)){
    x <- group_data_total[i,]
    x1 <- group_data[group_data$conditionId==x["conditionId"][[1]] & group_data$error==1,]
    if(nrow(x1)==0){
      cat(toString(x["conditionId"][[1]]), " error rate is ", 0, ", time is ",x["time"][[1]],"\n")
    }else{
      cat(toString(x["conditionId"][[1]]), " error rate is ", x1["count"][[1]]/x["count"][[1]], ", time is ",x1["time"][[1]],"\n")
    }
  }
  
}
#write.csv(data_total, paste(file_path, "statics.csv", sep = ""))
cat("\n", "average time is ", toString(mean(total_time)/60), "min\n")
mean_time <- (sum(total_time)-max(total_time)-min(total_time))/(length(total_time)-2)
cat("average time (remove max and min) is ", toString(mean_time/60), "min\n")
cat("max time is ", toString(max(total_time)), "\n")
cat("min time is ", toString(min(total_time)), "\n")

# Uncomment if want to check the trial numbers per participant.
# temp <- data_total %>%
#   group_by(userName) %>%
#   summarise(trials = n()) %>%
#   filter(trials != 30)

# Prep Plot Consistency
data_total <- data_total %>%
  mutate(conditionName = conditionId) %>%
  mutate(conditionMagnitude = conditionId)
data_total[data_total$conditionId==0, ]$conditionName <- "Random Assignment"
data_total[data_total$conditionId==1, ]$conditionName <- "Optimized Assignment"
data_total[data_total$conditionId==2, ]$conditionName <- "Alpha Blending"
data_total[data_total$conditionId==3, ]$conditionName <- "C3-Palette Assignment"
data_total[data_total$conditionId==4, ]$conditionName <- "Palettailor"
data_total[data_total$conditionId==5, ]$conditionName <- "C3-Palette Generation"

data_total <- data_total %>%
  mutate(conditionName = fct_relevel(conditionName, 
                                 "C3-Palette Generation",
                                 "Palettailor", "C3-Palette Assignment", 
                                 "Alpha Blending", "Optimized Assignment", "Random Assignment"))

condition_names <- c("Random Assignment", "Optimized Assignment", "Alpha Blending", "C3-Palette Assignment", "Palettailor", "C3-Palette Generation")
# 0 is small, 1 is medium, 2 is large
for(i in 1:6){
  for(j in 0:2){
    data_total[data_total$conditionId==(i-1) & data_total$changeMagnitude==j, ]$conditionMagnitude <- paste(condition_names[i], j, sep = "-")
  }
}


# compute the time threshold
data_time_correct <- data_total[data_total$error==0, ]
data_time_threshold_correct <- data_total[data_total$totalTime<=30 & data_total$error==0, ]
threshold <- nrow(data_time_threshold_correct)/nrow(data_time_correct)
cat("time threshold is ", threshold, "\n")

```

## CI Plots and Statistical Tests
```{r}

data <- data_total

#Statistical Test Results: mu~95% CI, W, p-value, d.
df_stat_output <- stat_table_m(data)
df_stat_output


ciplot(data, "error", "conditionName", "Total")
saveImg("results/coseparability-error-conditionName-total.pdf")
ciplot(data, "accuracy", "conditionName", "Total")
saveImg("results/coseparability-accuracy-conditionName-total.pdf")
ciplot(data, "totalTime", "conditionName", "Total")
saveImg("results/coseparability-totalTime-conditionName-total.pdf")


data <- data %>%
  mutate(conditionMagnitude = fct_relevel(conditionMagnitude, 
                                 "C3-Palette Generation-0", "Palettailor-0", "C3-Palette Assignment-0", "Alpha Blending-0", "Optimized Assignment-0", "Random Assignment-0",
                                 "C3-Palette Generation-1", "Palettailor-1", "C3-Palette Assignment-1", "Alpha Blending-1", "Optimized Assignment-1", "Random Assignment-1",
                                 "C3-Palette Generation-2", "Palettailor-2", "C3-Palette Assignment-2", "Alpha Blending-2", "Optimized Assignment-2", "Random Assignment-2"))

ciplotManual(data, "error", "conditionMagnitude", "Magnitude")
saveImg("results/coseparability-error-conditionMagnitude-total.pdf")
ciplotManual(data, "accuracy", "conditionMagnitude", "Magnitude")
saveImg("results/coseparability-accuracy-conditionMagnitude-total.pdf")
ciplotManual(data, "totalTime", "conditionMagnitude", "Magnitude")
saveImg("results/coseparability-totalTime-conditionMagnitude-total.pdf")


if(nrow(data[data$changeType=="pos", ])>0){
  ciplot(data[data$changeType == "pos",], "error", "conditionName", "pos")
  saveImg("results/coseparability-error-conditionName-pos.pdf")
  ciplot(data[data$changeType == "pos",], "totalTime", "conditionName", "pos")
  saveImg("results/coseparability-totalTime-conditionName-pos.pdf")
  
  ciplot(data[data$changeType == "num",], "error", "conditionName", "num")
  saveImg("results/coseparability-error-conditionName-num.pdf")
  ciplot(data[data$changeType == "num",], "totalTime", "conditionName", "num")
  saveImg("results/coseparability-totalTime-conditionName-num.pdf")
  
  ciplotManual(data[data$changeType == "pos",], "error", "conditionMagnitude", "pos")
  saveImg("results/coseparability-error-conditionMagnitude-pos.pdf")
  ciplotManual(data[data$changeType == "pos",], "totalTime", "conditionMagnitude", "pos")
  saveImg("results/coseparability-totalTime-conditionMagnitude-pos.pdf")
  
  ciplotManual(data[data$changeType == "num",], "error", "conditionMagnitude", "num")
  saveImg("results/coseparability-error-conditionMagnitude-num.pdf")
  ciplotManual(data[data$changeType == "num",], "totalTime", "conditionMagnitude", "num")
  saveImg("results/coseparability-totalTime-conditionMagnitude-num.pdf")
}



```


## Power Analysis
### error
```{r}
data <- data_total#[data_total$changeType=="pos", ]

#error
df1 <- data %>% 
  filter(conditionName == "C3-Palette Generation") %>% 
  select(error) 
df2 <- data %>%
  filter(conditionName == "Alpha Blending") %>% 
  select(error) 

abs(mean(df1$error) - mean(df2$error))
df <- df1 %>% rbind(df2)

powerAnalysisGraph(mean(df1$error), mean(df2$error), sd(df$error))
saveImg("results/coseparability-error-conditionName-powerAnalysis.pdf")
```